Group 9 Paper

### 2021-12-16 paper.Rmd
added code for rf

This will be the section on Random Forest. Include discussion on how & why you chose to do it the way you did it.

>>>>

```{r}
rf_fit <- randomForest(as.factor(HeartDisease) ~ ., data = train, mtry = sqrt(ncol(train)-1), importance = TRUE, type= "classification", ntrees=1000)

true <- test$HeartDisease
rf <- predict(rf_fit,test,type="class")

confm2<-table(predicted=rf,True=true)
confm2

paste(" Test Accuracy :",(confm2[1,1]+confm2[2,2])/sum(confm2))

overall_RF <- (confm2[1,1]+confm2[2,2])/sum(confm2)
rf_fit

imp<-data.frame(rf_fit$importance)

imp$variables <- rownames(imp)
rownames(imp) <- 1:nrow(imp)

imp <- imp[order(imp$MeanDecreaseAccuracy),]
```
